Verifying Demonstrations

### 2020-05-07 paper/protocol-trusted.tex
Slight clarifications

>>>>

The key~\(\sk\) can be used together with \(\ACprf\) to create a 
pseudonym~\(p\gets \ACprf[_k][c]\) in a particular context~\(c\) (see 
\cref{ACprfAlg}).
There exists \iac{PK} such that one can prove that \(p\) is computed correctly 
from \(c\) with a valid key~\(\sk\) (see \cref{ACprfPKalg} or \cite{AnonPass} 
for details).
